The Analog Method for Precipitation Downscaling: Finding Better Analog Situations at a Sub-Daily Time Step

### 2016-10-13 Moving temporal window - HESS/template.tex
Removing some tables.

Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered. The AM parameters were calibrated using AtmoSwing \citep{Horton2016} on the original archive (Tables \ref{table:params_2Z} and \ref{table:params_2Z-2MI}) and will be used thereafter.

@@

After recalibrating, some changes in the optimal parameters can be observed for both 2Z (Table \ref{table:params_2Z_new}) and 2Z-2MI methods (Table \ref{table:params_2Z-2MI_new}). Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease. More significantly, the optimal number of analogs increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method. The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station. It seems as if the method perceive the increase in the archive length and diversity by allowing to extract more analogs. As we saw in Fig. \ref{fig:changes_S1}, the improvement of the $S_{\text{TW}}$ criteria grows along with the rank of the analog, which shows an accumulation of better analog situations in the distributions. It seems thus profitable to widen the selection of analogs in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values. The number of good analogs is thus globally increased.

@@

\begin{table}[htb]
	\caption{Calibrated parameters (spatial windows and number of analogs) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) and skill score (\%) of the method on the full archive.}
	\begin{center}
		\begin{tabular}{l c c c c }
			\hline
			Station & Long (° E) & Lat (° N) & $N_{1}$ & $S_{\text{SCRP}}$ \\
			\hline
			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 47.5 & 40 & 30.73 \\
			Zermatt & 0 $\rightarrow$ 20 & 37.5 $\rightarrow$ 50 & 35 & 23.87 \\
			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 47.5 & 30 & 25.11 \\
			Montana & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 32.55 \\
			Sion & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 26.23 \\
			Aigle & -5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 50 & 30.59 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z}
\end{table}

\begin{table}[htb]
	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) on the complete archive. The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogs of the first analogy level ($N_{1}$), which are here different. The $5^{th}$ column is the number of analogs for the second level ($N_{2}$).}
	\begin{center}
		\begin{tabular}{l c c c c c }
			\hline
			Station & Long (° E) & Lat (° N) & $N_{1}$ & $N_{2}$ & $S_{\text{SCRP}}$ \\
			\hline
			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 60 & 25 & 34.31 \\
			Zermatt & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 55 & 25 & 28.28 \\
			Visp & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 45 & 25 & 28.85 \\
			Montana & 5 $\rightarrow$ 7.5 & 45 $\rightarrow$ 47.5 & 55 & 30 & 36.11 \\
			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 90 & 30 & 31.16 \\
			Aigle & 7.5 & 45 $\rightarrow$ 47.5 & 100 & 35 & 35.82 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z-2MI}
\end{table}

@@

\begin{table}[htb]
	\caption{Calibrated parameters (spatial windows and number of analogs) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) with the MTW approach.}
	\begin{center}
		\begin{tabular}{l c c c }
			\hline
			Station & Long (° E) & Lat (° N) & $N_{1}$ \\
			\hline
			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 50 & 50 \\
			Zermatt & 0 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 55 \\
			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 50 & 55 \\
			Montana & -2.5 $\rightarrow$ 15 & 42.5 $\rightarrow$ 47.5 & 55 \\
			Sion & -2.5 $\rightarrow$ 15 & 37.5 $\rightarrow$ 50 & 55 \\
			Aigle & -2.5 $\rightarrow$ 15 & 40 $\rightarrow$ 50 & 75 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z_new}
\end{table}

\begin{table}[htb]
	\caption{Parameters of the moisture variables from the 2Z-2MI method with the MTW approach. The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogs of the first analogy level ($N_{1}$), which are here different. The $5^{th}$ column is the number of analogs for the second level ($N_{2}$).}
	\begin{center}
		\begin{tabular}{l c c c c }
			\hline
			Station & Long (° E) & Lat (° N) & $N_{1}$ & $N_{2}$ \\
			\hline
			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 110 & 35 \\
			Zermatt & 7.5 & 45 $\rightarrow$ 47.5 & 80 & 30 \\
			Visp & 7.5 & 45 $\rightarrow$ 47.5 & 135 & 35 \\
			Montana & 5 $\rightarrow$ 7.5 & 45 & 110 & 40 \\
			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 140 & 50 \\
			Aigle & 5 $\rightarrow$ 7.5 & 45 & 135 & 45 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z-2MI_new}
\end{table}

>>>>

Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered. The AM parameters were calibrated using AtmoSwing \citep{Horton2016} on the original archive (Tables \ref{table:performance}) and will be used thereafter.

@@

After recalibrating, some changes in the optimal number of analogs can be observed for both 2Z and 2Z-2MI methods (Table \ref{table:nb_analogs_new}). Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease. More significantly, the optimal number of analogs increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method. The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station. It seems as if the method perceive the increase in the archive length and diversity by allowing to extract more analogs. As we saw in Fig. \ref{fig:changes_S1}, the improvement of the $S_{\text{TW}}$ criteria grows along with the rank of the analog, which shows an accumulation of better analog situations in the distributions. It seems thus profitable to widen the selection of analogs in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values. The number of good analogs is thus globally increased.

@@

\begin{table}[htb]
	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) and skill score (\%) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), on the full archive.}
	\begin{center}
		\begin{tabular}{l c c c c c }
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{3}{c}{2Z-2MI} \\
			& $N_{1}$ & $S_{\text{SCRP}}$ & $N_{1}$ & $N_{2}$ & $S_{\text{SCRP}}$ \\ 
			\hline
			Ulrichen & 40 & 30.73 & 60 & 25 & 34.31 \\
			Zermatt & 35 & 23.87 & 55 & 25 & 28.28 \\
			Visp & 30 & 25.11 & 45 & 25 & 28.85 \\
			Montana & 40 & 32.55 & 55 & 30 & 36.11 \\
			Sion & 40 & 26.23 & 90 & 30 & 31.16 \\
			Aigle & 50 & 30.59 & 100 & 35 & 35.82 \\ 
			\hline
		\end{tabular}
	\end{center}	
	\label{table:performance}
\end{table}

@@

\begin{table}[htb]
	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), using the MTW approach.}
	\begin{center}
		\begin{tabular}{l c c c }
			\hline
			\multirow{2}{*}{Station} & \multicolumn{1}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& $N_{1}$ & $N_{1}$ & $N_{2}$ \\ 
			\hline
			Ulrichen & 50 & 110 & 35 \\
			Zermatt & 55 & 80 & 30 \\
			Visp & 55 & 135 & 35 \\
			Montana & 55 & 110 & 40 \\
			Sion & 55 & 140 & 50 \\
			Aigle & 75 & 135 & 45 \\ 
			\hline
		\end{tabular}
	\end{center}	
	\label{table:nb_analogs_new}
\end{table}
